\malg: a novel interest management algorithm for distributed simulations of MMOGs

### 2008-05-13 textos/dsrt/engaoi.tex
related work done

@@

The algorithms described in the following sections are mainly based on the euclidian distance between each avatar and all other entities in the virtual environment. This could create a scalability problem due to the processing of the distances, but a distributed architecture is assumed, where the processing can and should be parallelized. In the distribution model defined previously, each server controls a region of the map. Therefore, each one of them manages only a subset of the entities of the game, checking only the distances between each pair of them, in addition to the entities that are in a neighbouring region, close to its border.

>>>>

%No que se refere a gerenciamento de interesse, trabalhos como \cite{morse1996iml, rak1996egb, zou2001egt, morgan2005imm} e \cite{minson2005aim} podem ser citados. Em \cite{rak1996egb}, é proposto um esquema de gerenciamento de interesse baseado em um ambiente virtual divido em células de uma grade. A cada célula está associado um grupo de multicast. Cada participante da simulação se subscreve então no grupo de multicast da célula onde ele se encontra, assim como de células vizinhas se estiverem ao alcance de sua visão. Cada participante envia então suas atualizações de estado ao grupo de multicast da região onde se encontra. %O problema desta abordagem é que não se pode assumir que haverá suporte a multicast sobre a Internet, já que não é amplamente estabelecido. Além disso, uma área de interesse formada por células fixas envolverá um número maior de objetos do que seria realmente necessário do que ocorreria se fosse utilizada uma área completamente dinâmica.

Regarding the interest management technique, works such as \cite{morse1996iml, rak1996egb, zou2001egt, morgan2005imm} and \cite{minson2005aim} may be cited. In \cite{rak1996egb}, it is proposed an interest management scheme based on a virtual environment divided into a grid of cells. Each cell is assigned to a multicast group. Each participant of the simulation subscribes then to the multicast group of the cell where he is, as well as of the neighboring cells if they are within his field of view. Each participant then sends his state updates to the multicast group of the region where he is.

%Em \cite{zou2001egt}, também  são considerados esquemas de gerenciamento de interesse baseados em grupos de multicast. É feita uma comparação entre a formação de grupos baseado em célula, onde cada um está associado a uma célula de uma grade que compõe o ambiente virtual, e agrupamento baseado em objetos, onde para cada objeto existe um grupo multicast associado. Verificou-se que há uma compensação (tradeoff) entre o custo das mensagens de controle dos grupos de multicast e o custo das mensagens de atualização de estado propriamente ditas.

In \cite{zou2001egt}, multicast-based interest management schemes are also considered. A comparison is made between cell-based grouping, where each group is associated with a cell of a grid that compose the virtual environment, and grouping based on objects, where there is a multicast group for each object. It was found that there is a tradeoff between the cost of multicast group formation control messages and the cost of the state updates themselves.

%Um esquema de gerenciamento de interesse que utiliza um middleware orientado a mensagens é apresentado em \cite{morgan2005imm}. Dentre outros aspectos, este esquema faz uma predição do que será o interesse de determinado participante no futuro, baseado na posição e vetor velocidade do mesmo no ambiente virtual. Dessa forma, cada um começa a receber atualizações de estado de entidades que não estão ainda ao alcance de sua visão, mas que provavelmente estarão em um futuro próximo, tornando seus estados disponíveis assim que elas estiverem dentro do campo de visão.

An interest management scheme using a message oriented middleware is presented in \cite{morgan2005imm}. This scheme predicts what will be of interest to a participant in the future, based on his current position and velocity vector in the virtual environment. Thus, each participant starts receiving state updates from entities that are not yet within his field of view, but probably will be in the near future, making their status available as soon as he can see them.

%por morse por último e justificar baseado nos parâmetros criados por ela.

%Em \cite{morse1996iml}, é feito um apanhado de sistemas que utilizam a técnica de gerenciamento de interesse, salientando quais critérios são utilizados por cada um. É apresentada então uma taxonomia de tais sistemas, classificando-os de acordo com: modelo de comunicação, foco da filtragem e domínios de responsabilidade. O modelo pode ser \textit{unicast}, \textit{multicast} ou \textit{broadcast}. %Como supõe-se aqui um sistema distribuído sobre a Internet, sobre a qual o suporte a \textit{multicast} não está ainda amplamente estabelecido, considera-se apenas o modelo de comunicação \textit{unicast}.
%O foco da filtragem refere-se a que tipo de características são observadas de cada objeto para realizar esta filtragem: podem ser \textit{intrínsecas}, como o valor de atributos do objeto (e.g. coordenadas exatas de sua localização), ou \textit{intrínsecas}, como a qual grupo multicast ele está associado. Por fim, o domínio de responsabilidade atribuída a um gerenciador de interesse, que verifica para quem cada estado é relevante, pode ser \textit{dinâmico} ou \textit{estático}. Por exemplo, se cada gerenciador é designado para controlar uma área fixa do ambiente virtual, seu domínio de responsabilidade é estático, mas se ele controla uma área que possa aumentar ou diminuir de tamanho, seu domínio de responsabilidade é dinâmico.

In \cite{morse1996iml}, it is made a survey of systems that use the interest management technique, describing the purpose, scope and what criteria are used by the management scheme employed by each one of them. It is then presented a taxonomy of such systems, classifying them according to: communication model, filtering focus and domain of responsibility. The model may be \textit{unicast}, \textit{multicast} or \textit{broadcast}. The filtering focus refers to what characteristics are observed for each object to perform the filtering: they may be \textit{intrinsic}, such as the values of the object's attributes (e.g. the exact coordinates of its location), or \textit{intrinsic}, such as which multicast group it is subscribed to. Finally, the domain of responsibility assigned to a interest manager, which checks for whom each state is relevant, can be \textit{static} or \textit{dynamic}. For instance, if an interest manager is assigned to a fixed area of the virtual environment, its domain of responsibility is static, but if he controls an area that may increase or decrease in size, its domain of responsibility is dynamic.

%por morse por último e justificar baseado nos parâmetros criados por ela.

%Levando em consideração que o modelo de comunicação multicast não é amplamente suportado na Internet \cite{elsayed2004alm}, tanto por razões técnicas quanto comerciais, neste trabalho optou-se por seguir o modelo unicast, considerando que cada broadcast consiste na verdade em um conjunto de sucessivas transmissões unicast, uma para cada destino. Além disso, %como o poder de processamento atualmente é maior que há uma década atrás, utiliza-se filtragem intrínseca e domínios de responsabilidade dinâmicos, para que haja maior precisão e, consequentemente, uma maior redução no tráfego de atualizações de estado \cite{morse1996iml}.

Taking into consideration that the multicast communication model is not widely supported in the Internet \cite{elsayed2004alm}, %for technical and marketing reasons as well,
 in this work we opted to follow the unicast model. Each broadcast consists then of a set of unicast transmissions, one for each destination. Moreover, intrinsic filtering and dynamic domain of resposibility were used, in order to increase the precision of the interest management and consequently achieve a greater reduction in the state update traffic \cite{morse1996iml}.

@@

The algorithms described in the following sections are mainly based on the euclidian distance between each avatar and all other entities in the virtual environment. This could create a scalability problem due to the processing of the distances, but a distributed architecture is assumed, where the processing can and should be parallelized. In the distribution model defined previously, each server controls a region of the map. Therefore, each one of them manages only a subset of the entities of the game, checking only the distances between each pair of them, in addition to the entities that are in a neighboring region, close to its border.
